### 2017-01-21 second-order-spsa-3.tex
quad thm chapter4 part1 slightly done

We next present a convergence rate result for the special case of a quadratic objective function under the following additional assumptions:
\begin{pvn}
\item  $f$ is quadratic and $\nabla^2 f(x^*) > 0$. 
\item The operator $\Upsilon$ is chosen such that $\E(\parallel \Upsilon(\overline H_n) - \overline H_n\parallel^2) = o(e^{-2wn^{1-r}/(1-r)})$ and \\$\parallel \Upsilon(H) - H \parallel^2 / (1+\parallel H \parallel^2)$ is uniformly bounded.
\end{pvn}
\begin{theorem}(\textbf{2SPSA-3-IH Quadratic case - Convergence rate})
\label{thm:spsaquad-bound}
Assume (A23), (A29), (A30) and (A31) and also that the setting is noise-free. 
Let $b_n = b_0/n^r$, $n=1,2,\ldots,k$, where $1/2 < r < 1$ and $0 < b_0 \leq 1$. For notational simplicity, let $H^*=\nabla^2 f(x^*)$. Letting $\Lambda_k = \overline H_k - H^*$, we have 
\text{trace}[\E (\Lambda_n \tr \Lambda_n)] = O(e^{-2b_0n^{1-r} / {1-r}}).
\label{eq:spsaquad-bigo}
\end{theorem}
\begin{proof}
Since the setting is noise-free with a quadratic objective, we can rewrite \eqref{eq:spsahnhat} as follows:
 \widehat H_n =    \nabla^2 f(\theta_n) +\Psi_{n}(\nabla^2 f(\theta_n)),\label{eq:spsahnhat-ext}
where $\Psi_n(H)$ is defined in \eqref{eq:psinhatspsa3}.
The proof involves the following steps:
\begin{description}
  \item[Step 1:] Here we prove the MSE convergence of $\overline H_k$, i.e., $\E [\Lambda_n\tr \Lambda_n] \rightarrow 0$ a.s. as $n\rightarrow \infty$.
  \item[Step 2:] We unroll the recursion \eqref{eq:2spsa-3-ih} and then derive a convenient representation for the  $\text{trace}[\E (\Lambda_n \tr \Lambda_n)]$.
  \item[Step 3:] We derive the main result in \eqref{eq:spsaquad-bigo} using a proof by contradiction. 
\end{description}
\noindent\textbf{Step 1: MSE convergence of $\overline H_n$} \\
This part in exactly the same manner as part (i) in Theorem 3 of \cite{spall-jacobian}.\\
By rewriting the \eqref{eq:2spsa-3-ih} in the following form
\begin{align}\label{eq:hhatexpanded}
\overline H_{n} &= \overline H_{n-1} - b_{n} ( \overline H_{n-1} - \widehat H_n + \widehat \Psi_n)\nonumber\\
&= \overline H_{n-1} - b_{n} ( \overline H_{n-1} - H^* + \widehat \Psi_n - \Psi_n (H^*))
The above equation can be thought as a stochastic approximation analogue of \eqref{eq:2spsa-3-ih}.

>>>>

We next present a convergence rate result for the special case of a quadratic objective function under the following additional assumptions:
\begin{pvn}
\item  $f$ is quadratic and $\nabla^2 f(x^*) > 0$. 
\item The operator $\Upsilon$ is chosen such that $\E(\parallel \Upsilon(\overline H_n) - \overline H_n\parallel^2) = o(e^{-2wn^{1-r}/(1-r)})$ and \\$\parallel \Upsilon(H) - H \parallel^2 / (1+\parallel H \parallel^2)$ is uniformly bounded.
\end{pvn}
\begin{theorem}(\textbf{2SPSA-3-IH Quadratic case - Convergence rate})
\label{thm:spsaquad-bound}
Assume (A23), (A29), (A30) and (A31) and also that the setting is noise-free. 
Let $b_n = b_0/n^r$, $n=1,2,\ldots,k$, where $1/2 < r < 1$ and $0 < b_0 \leq 1$. For notational simplicity, let $H^*=\nabla^2 f(x^*)$. Letting $\Lambda_k = \overline H_k - H^*$, we have 
\begin{align}
\text{trace}[\E (\Lambda_n \tr \Lambda_n)] = O(e^{-2b_0n^{1-r} / {1-r}}).
\label{eq:spsaquad-bigo}
\end{align}
\end{theorem}
\begin{proof}
Since the setting is noise-free with a quadratic objective, we can rewrite \eqref{eq:spsahnhat} as follows:
\begin{align}
 \widehat H_n &=    \nabla^2 f(\theta_n) +\Psi_{n}(\nabla^2 f(\theta_n))\nonumber\\
 &=    \nabla^2 f(\theta^*) +\Psi_{n}(\nabla^2 f(\theta_n))\nonumber\\
 &=    H^* +\Psi_{n}(H^* ),\label{eq:spsahnhat-ext}
\end{align}
where $\Psi_n(H)$ is defined in \eqref{eq:psinhatspsa3}.
The proof involves the following steps:
\begin{description}
  \item[Step 1:] Here we prove the MSE convergence of $\overline H_k$, i.e., $\E [\Lambda_n\tr \Lambda_n] \rightarrow 0$ a.s. as $n\rightarrow \infty$.
  \item[Step 2:] We unroll the recursion \eqref{eq:2spsa-3-ih} and then derive a convenient representation for the  $\text{trace}[\E (\Lambda_n \tr \Lambda_n)]$.
  \item[Step 3:] We derive the main result in \eqref{eq:spsaquad-bigo} using a proof by contradiction. 
\end{description}
\noindent\textbf{Step 1: MSE convergence of $\overline H_n$} \\
This part in exactly the same manner as part (i) in Theorem 3 of \cite{spall-jacobian}.\\
By rewriting the \eqref{eq:2spsa-3-ih} in the following form
\begin{align}\label{eq:hhatexpanded}
\overline H_{n} &= \overline H_{n-1} - b_{n} ( \overline H_{n-1} - \widehat H_n + \widehat \Psi_n)\nonumber\\
&= \overline H_{n-1} - b_{n} ( \overline H_{n-1} - H^* + \widehat \Psi_n - \Psi_n (H^*))
\end{align}
The above equation can be thought as a stochastic approximation analogue of \eqref{eq:2spsa-3-ih}. The above stochastic approximation algorithm aimed at finding the roots of the equation $H-H^*=0$. In \eqref{eq:hhatexpanded}, $\E (\widehat \Psi_n - \Psi_n (H^*) | \F_n) = 0 \,\,\ a.s$.  Given a Lyapunov function, by showing the conditions required to show   the mean square convergence of the \eqref{eq:hhatexpanded} from the \cite{nevel1973stochastic}, pp. 92-94. From part (i) in Theorem 3 of \cite{spall-jacobian}, one can check that our algorithm indeed satisfy those conditions,  which in turn implies the $\E [\Lambda_n\tr \Lambda_n] \rightarrow 0$ a.s. as $n\rightarrow \infty$.
